---
title: "Assignment B1"
author: "Christina"
date: "10/31/2021"
output: github_document
---

```{r}
suppressPackageStartupMessages(library(datateachr)) 
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(testthat))
```

Before starting, let's make some simple tribbles of temperature data for our later examples:
```{r}
tempC <- tribble(
  ~x, ~Celsius, 
  "a", 20, 
  "b", 17,
  "c", 25,
)

tempCF <- tribble(
  ~x, ~Celsius, ~Fahrenheit,
  "a", 20, 68,
  "b", 17, 62.6,
  "c", 25, 77,
)
```


Exercise 1 and 2: Make a function and write documentations
** Make a function that takes in a vector of temperature numbers and convert it to another temperature unit. There are three options for the input unit and output unit: Fahrenheit, Celsius and Kelvin.

 
```{r}
#' Convert a numerical representation of temperature between three units: Fahrenheit, Celsius and Kelvin.
#' 
#' @param input_unit unit of the input temperature; The name input_unit indicates that it's the unit of our input temperature
#' @param output_unit unit of the output temperature; The name output_unit indicates that it's the unit of our output temperature
#' @return the converted temperature in the specified output unit

temperature_conversion <- function(input_unit, output_unit, input_temp) {
  if (!((input_unit == "C") | (input_unit == "Celsius") | (input_unit == "K") | (input_unit == "Kelvin") | (input_unit == "F") | (input_unit == "Fahrenheit"))) {
    stop("Input unit invalid, must be one of Fahrenheit, Celsius, Kelvin or F, C, K")
  }
  if (!((output_unit == "C") | (output_unit == "Celsius") | (output_unit == "K") | (output_unit == "Kelvin") | (output_unit == "F") | (output_unit == "Fahrenheit"))) {
    stop("Output unit invalid, must be one of Fahrenheit, Celsius, Kelvin or F, C, K")
  }
  
  output_temp = case_when((input_unit == "C" | input_unit == "Celsius") & (output_unit == "K" | (output_unit == "Kelvin")) ~ input_temp + 273.15,
                          (input_unit == "K" | input_unit == "Kelvin") & (output_unit == "C" | (output_unit == "Celsius")) ~ input_temp - 273.15,
                          (input_unit == "F" | input_unit == "Fahrenheit") & (output_unit == "C" | (output_unit == "Celsius")) ~ (input_temp - 32) * 5 / 9,
                          (input_unit == "C" | input_unit == "Celsius") & (output_unit == "F" | (output_unit == "Fahrenheit")) ~ (input_temp * 9 / 5) + 32,
                          (input_unit == "F" | input_unit == "Fahrenheit") & (output_unit == "K" | (output_unit == "Kelvin")) ~ (input_temp - 32) * 5 / 9 + 273.15,
                          (input_unit == "K" | input_unit == "Kelvin") & (output_unit == "F" | (output_unit == "Fahrenheit")) ~ ((input_temp - 273.15) * 9 / 5) + 32,
                          TRUE ~ NA_real_)
  return (output_temp)
}
``` 

Exercise 3: Include examples 
```{r}
#' @examples
#' temperature_conversion("Celsius", "Kelvin", 50)
#' # Here we convert 50 degree Celsius into Kelvin. We need to input the input_unit "Celsius", the output_unit "Kelvin", and the temperature before conversion "50". The value returned from calling the function is thus our temperature in Kelvin.
#' 
#' temperature_conversion("K", "F", 50)
#' # Here we convert 50 degree Kelvin into Fahrenheit. We need to input the input_unit "K" which is another valid input representing "Kelvin", the output_unit F representing "Fahrenheit", and the temperature before conversion "50". The value returned from calling the function is thus the temperature in Fahrenheit.
#' 
#' mutate(temp, Fahrenheit = temperature_conversion("C", "F", Celsius))
# Here we take in a dataset with a column of temperature in Celsius, and convert each temperature into Fahrenheit using the temperature_conversion function. The result will have a new column containing each corresponding Fahrenheit temperature value.
```


Exercise 4: Test the Function
```{r}
test_that("Different input types", {
  expect_equal(temperature_conversion("Celsius", "Kelvin", 100), 373.15 , tolerance = 1e-4)
  expect_equal(temperature_conversion("F", "C", 50), 10, tolerance = 1e-4)
  expect_equal(temperature_conversion("Kelvin", "F", 10), -441.67, tolerance = 1e-4)
  
})

test_that("NA input data values", {
  expect_equal(temperature_conversion("Kelvin", "F", NA), NA_real_)
  
})

test_that("Invalid input_unit or output_unit", {
  expect_error(temperature_conversion("Kelvin", "Cels", 10))
})

test_that("Operate on column variable of a dataset", {
  expect_equal(mutate(tempC, Fahrenheit = temperature_conversion("C", "F", Celsius)), tempCF, tolerance = 1e-4)
})

```

